Lens Modeling in \sw

### 2014-06-21 text/ms.tex
editing

\newcommand{\apj}{ApJ}
\newcommand{\apjs}{ApJS}
\newcommand{\apjl}{ApJL}
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\mnras}{MNRAS}
\newcommand{\aj}{AJ}
\newcommand{\araa}{ARAA}
\newcommand{\pasp}{PASP}
\newcommand{\pasj}{PASJ}

@@

In \secref{Fermat}, for the sake of a more intuitive
explanation, we suppressed some constant factors in
equations \eqref{eq:Ageom}, \eqref{eq:Aarriv} and \eqref{eq:Poisson}.
Here we fill in the details.

First let us recall various distance formulas. Comoving distances
involve integrals of the type
\begin{equation}
\int \frac{dz}{\sqrt{\Omega_m(1+z)^3 + \Omega_\Lambda}}
%\raise.5ex\hbox{.}
\end{equation}
Specifically, the comoving distance $D_S$ from observer to source,
$D_{LS}$ from lens to source, and $D_L$ from observer to lens are
given by the above integral, with limits as follows.
\begin{equation}
\begin{aligned}
&D_S    &                                &\int_0^{z_S} \\
\noalign{\medskip}
&D_{LS} & = \frac c{H_0} \ \times \quad  &\int_{z_L}^{z_S} \\
\noalign{\medskip}
&D_L    &                                &\int_0^{z_L}
\end{aligned}
\end{equation}
Angular-diameter distances $d$ can be related to comoving distances
$D$ by scale factors, as follows.
\begin{equation}
\begin{aligned}
D_S &= (1+z_S) \, d_S \\
D_{LS} &= \frac{1+z_S}{1+z_L} \, d_{LS} \\
D_L &= (1+z_L) \, d_L
\end{aligned}
\end{equation}
Consequently, angular-diameter distances are always smaller than
comoving distances.  Moreover, while comoving distances can be simply
added, angular distances cannot:
\begin{equation}
d_S \neq d_L + d_{LS}
\end{equation}

Locations on the lens plane in angular coordinates on the sky, are
expressed as
\begin{equation}
(x,y) = d_L (\theta_x,\theta_y)
\end{equation}

The $A$ areas (with the implicit
constant factor that makes them time delays) and the $\kappa$ density are related to physical arrival
time $t$ and density $\Sigma$ as
\begin{equation}
\begin{aligned}
A           &= \frac{c}{(1+z_L)^2} \frac{D_L D_{LS}}{D_S} \times t \\
\kappa(x,y) &= \frac{4\pi G}{c^2} \frac{D_L D_{LS}}{D_S}
               \times \Sigma(x,y)
\end{aligned}
\end{equation}
Letting the source be offset at $(s_x,s_y)$ rather than at the
origin, we have
\begin{equation}
\begin{aligned}
t_{\rm geom} &= \frac{(1+z_L)^2}{2c} \frac{D_S}{D_L D_{LS}}
\left( (x-s_x)^2 + (y-s_y)^2 \right) \\
\nabla^2 t_{\rm grav} &= -(1+z_L)\frac{8\pi G}{c^3} \, \Sigma(x,y)
\end{aligned}
\end{equation}
We can now compare with equations (2.1) to (2.6)
from \cite{1986ApJ...310..568B}.
%% comparison to be explicited

\section{Miscellaneous}

Maybe discard \figref{ER_all_models}, since the essential information is there in \figref{ER_per_sim}.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.90\linewidth]{fig/eR_1}
  \caption{\ERf for all models with estimated errors in blue squares, \ERg of simulation in red crosses}
  \label{fig:ER_all_models}
\end{figure}

>>>>

\newcommand{\apj}{ApJ}
\newcommand{\apjs}{ApJS}
\newcommand{\apjl}{ApJL}
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\mnras}{MNRAS}
\newcommand{\aj}{AJ}
\newcommand{\araa}{ARAA}
\newcommand{\pasp}{PASP}
\newcommand{\pasj}{PASJ}
\newcommand{\nat}{Nature}
\newcommand{\nar}{New Astr Rev}

@@

### 2014-06-21 text/partA.tex
editing

A challenge set of 29 was selected, representing the different image
morphologies among the spacewarps sims.  Modellers then contributed
129 models for these sims (at least for each sim).  Models were
collecting in the same forum used to model real candidate lenses, and
under the same conditions --- modellers were free to consult and
refine each other's models, but had no information on how the sims
were generated.

@@

The modellers proposed a total of 129 models for the 29 sims in the
challenge. Typically XX models were produced per simulation, with XX
systems having only XX models (corresponding tot he most simplest
simulations) to XX having XX models (a complex and contrversial lens
system). In the following we discuss eight example lenses in detail
with individual notes per system and corresponding plots are shown in
figures 4-11 (or whatever compact version you end up making). These
eight examples were chosen on the basis of …??

The modelers proposed a total of 129 models for the 29 sims in the
challenge.  Figures \ref{fig:6941} to \ref{fig:6919} show eight of
models in some detail.

>>>>

A challenge set of 29 was selected, representing the different image
morphologies among the spacewarps sims.  Modellers then contributed
119 models for these sims (at least for each sim).  Models were
collecting in the same forum used to model real candidate lenses, and
under the same conditions --- modellers were free to consult and
refine each other's models, but had no information on how the sims
were generated.

@@

The modellers proposed a total of 119 models for the 29 sims in the
challenge. Typically XX models were produced per simulation, with XX
systems having only XX models (corresponding tot he most simplest
simulations) to XX having XX models (a complex and contrversial lens
system). In the following we discuss eight example lenses in detail
with individual notes per system and corresponding plots are shown in
figures 4-11 (or whatever compact version you end up making). These
eight examples were chosen on the basis of …??

The modelers proposed a total of 119 models for the 29 sims in the
challenge.  Figures \ref{fig:6941} to \ref{fig:6919} show eight of
models in some detail.

### 2014-06-21 text/partB.tex
stats of RE
editing

\Figref{ER_per_sim} shows that the calculated \ERf of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for good models.
One of the reasons for this is that it is hard to get the center of the lens on spot.
An offset leads to a flatter mass profile for the model compared to the simulation.

@@

We thank the Swiss Society for Astrophysics and Astronomy and the
Swiss Academy of Sciences.

>>>>

\Figref{ER_per_sim} shows that the calculated \ERf of the models tend
to be too high.  The overshoot varies from around 0.2 to 0.4 for good
models.  Discounting the models which were flagged by the users as
poor, \ERf{E,rec} is overestimated.  The mean and standard deviation
of the overestimate are 25\% and 20\%.  The models by an expert also
show a similar bias, having mean and standard deviation of the
overestimate being 20\% and 8\%.
One of the reasons for this is that it is hard to get the center of the lens on spot.
An offset leads to a flatter mass profile for the model compared to the simulation.

@@

We thank the Swiss Society for Astrophysics and Astronomy and the
Swiss Academy of Sciences. AV is supported by a research fellowship
from the Leverhulme Trust.
